---
title: 'Exercise #3'
author: "Oleg Tolochko (12552516), Tobias Anzinger (12615518)"
date: "`r Sys.Date()`"
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### d)
Strengths:
 - very fast/efficient
 - popular, standard in industry
 
Weaknesses:
 - Merging can cause issues 
 - difficult to use for beginners?
 
## Exercise 2

### a)
 https://github.com/Ballmaid/exeRcise-sheet-3


## Exercise 3

### b)

```{r message=FALSE, warning=FALSE}
library(tidyverse)
vornamen_2021 <- read.csv("data/vornamen_2021.csv")
vornamen_2022 <- read.csv("data/open_data_portal_2022.csv")

#names, that exist less than 4 times are named "4 oder weniger", which is not numeric

vornamen_2021$Anzahl <- ifelse(vornamen_2021$Anzahl == "4 oder weniger", 1, vornamen_2021$Anzahl)
vornamen_2021$Anzahl <- as.numeric(vornamen_2021$Anzahl)

vornamen_2022$Anzahl <- ifelse(vornamen_2022$Anzahl == "4 oder weniger", 1, vornamen_2022$Anzahl)
vornamen_2022$Anzahl <- as.numeric(vornamen_2022$Anzahl)
```
All names that are marked as "4 oder weniger" were converted to exactly 1. Most of the names listed probably will only exist exactly once, judging by the extreme decline in numbers. Else the majority of names listed in the data set would be falsly marked as more than one.

### c)
```{r message=FALSE, warning=FALSE}
sum(vornamen_2021$Anzahl)
sum(vornamen_2022$Anzahl)
```
2021 had more babies than 2022

### c)
```{r message=FALSE, warning=FALSE}
vornamen_2021$year <- 2021
vornamen_2022$year <- 2022
```

### d)
```{r message=FALSE, warning=FALSE}
vornamen <- bind_rows(vornamen_2021, vornamen_2022)
```

### e)
```{r message=FALSE, warning=FALSE}
library(knitr)
vornamen_combined <- vornamen %>%
  group_by(Vorname) %>%
  summarize(total_count = sum(Anzahl)) %>%
  arrange(desc(total_count))

kable(head(vornamen_combined, 10), caption = "Top 10 Most Popular Baby Names in Munich (2021-2022)")
```
## Exercise 4

### a)
```{r message=FALSE, warning=FALSE}
###Create a sample data frame
tax_data <- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks 1980", "Bavarian Circus"),
Tax_2019 = c(5000, 4000, 6000, 3500), Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800,
5900, 3400) )

# Calculate column-wise means
column_means <- lapply(tax_data[, -1], mean)
column_means

# Calculate row-wise means
tax_data$mean_tax <- rowMeans(tax_data[, -1])
tax_data


```


### b) 
rapply() is a recursive version of the lapply function. With it you can apply a function to each element in the list. The how parameter allows you to choose what will happen with the list

Example:
```{r message=FALSE, warning=FALSE}
nested_list <- list(a = 1:5, 
                    b = list(b1 = 6:10, b2 = 11:15), 
                    c = 16:20)
print(nested_list)

new_list <- rapply(nested_list, function(x) x * 2, how = "replace")


print(new_list)

```
In this case all the Elements in the list are doubled and replaced.